\documentclass{article}
\usepackage{parskip} %gives 1.5 spacing
\usepackage{graphicx,rotating,multicol}
\usepackage[colorlinks=true,urlcolor=blue,linkcolor=.]{hyperref}
\usepackage[margin=2.5cm]{geometry} %adjust page margins

\newcommand{\HRule}{\rule{\linewidth}{0.5mm}}
\begin{document}

\begin{center} 

\textbf{\huge{DENNIS LIU}}
\\[0.5cm]

tdennisliu@gmail.com \\
\url{tdennisliu.github.io}\\
\small{\url{www.linkedin.com/in/dennis-liu-5037}} \\
\small{\url{github.com/tdennisliu}}

\end{center}
%\emph{To enact positive change and understand the greater world community}
\begin{flushright}
Australian, engineer, data scientist 	
\end{flushright}

%\HRule


\HRule

\begin{multicols}{2}

\textbf{\emph{Education}}

\textbf{ The University of Adelaide} 

\emph{Ph.D candidate: Mathematics (Statistics)}\\
 \texttt{2017 to present}
\hypersetup{urlcolor=black}
\begin{itemize}
	\item Utilising Bayesian statistical learning,
	\item Proficiency in Python and standard quantitative packages (numpy, pandas, sklearn etc.),
	\item Developing novel models and construct appropriate learning algorithms to infer parameters,
	\item Applying object-orientated programming to improve interpretability. Click \href{https://tdennisliu.github.io/tutorials/1-simple-search-and-recursion.html#Towers-of-Hanoi}{here for more}.
\end{itemize}


%\textbf{\large Pulteney Grammar School} 

%\emph{SACE}\hfill \texttt{2004 to 2008}
%{\footnotesize
%\begin{itemize}
%\item Merits in Chemistry, Mathematical Studies and Specialist Mathematics
%\item TER of 99.85
%\item EE Scarfe Memorial Prize for Specialist Mathematics
%\item Participant in Australian Intermediate Mathematics Olympiad 

%\end{itemize}
%}

\textbf{\emph{Awards \& Achievements}}

\centering
\begin{tabular}{ p{6.75cm} p{0.25cm} }
Australian winner of the ActInSpace$^\tiny{\textregistered}$ challenge & \texttt{2020} \\
Invited speaker to WHO Pacific Region COVID-19 Science and Research Seminar & \texttt{2020} \\
ARC Centre of Excellence for Mathematical and Statistical Frontiers Public Lecture & \texttt{2019}\\
Data to Decisions CRC {Big Data Scholarship} &  \texttt{2017} \\
Dean's Merit Certificate for Outstanding Academic Achievement & \texttt{2009- 2012} \\

Max \& Bette Mendelson Foundation Scholarship & \texttt{2010}\\

\end{tabular}
\end{multicols}


My research focuses on building frameworks to model social behaviour and infectious diseases using digital, non-traditional datasets. I am interested in analysing human behaviour and examining their effects on models and forecasts of public health measures. \\

\emph{B. Ma. Comp. Sci (Applied)} \hfill  \texttt{2011- 2015}

%{\footnotesize
%\begin{itemize}
%\item Overloaded course work 2011 to 2012, studied part time while working full time 2014 to 2015
%\end{itemize} }

\emph{B. Eng. (Chemical) with First Class Honours} \hfill \texttt{2009- 2013}

\\
\HRule

\textbf{\emph{Publications \& Conferences}}
\begin{table}[h!] \small
\begin{tabular}{ p{12.1cm} c r}

\href{https://www.doherty.edu.au/uploads/content_doc/Technical_report_4_update_29July2020.pdf"}{
        Estimating temporal variation in transmission of SARS-CoV-2 and physical distancing behaviour in Australia.} \emph{The Doherty Institute} && \texttt{2020}\\

\href{https://theconversation.com/how-to-flatten-the-curve-of-coronavirus-a-mathematician-explains-133514}{How to flatten the curve of coronavirus, a mathematician explains.} \emph{The Conversation} & & \texttt{2020} \\
	
 \href{https://www.sciencedirect.com/science/article/pii/S175543652030030X}{Elucidating user behaviours in a digital health surveillance system to correct prevalence estimates.} \emph{Epidemics} & & \texttt{2020} \\

 Predicting influenza testing associated with family doctors by using a web-based surveillance system. & & \texttt{Acceptance pending} \\

 \href{https://chdsummerschool.com/}{Complex Human Data Summer School} & & \texttt{2018} \\

\end{tabular}
\end{table}



\HRule

{\footnotesize EMPLOYMENT EXPERIENCE}
\\

\textbf{\large Santos Ltd.}

\emph{Unit Controller Engineer} \hfill \texttt{2015 to 2017}

{\footnotesize
My previous employment required me to work in a remote location in a gas plant control room, where gas production is to be processed all hours of the day.

\begin{itemize}
\item Communicate issues with other stakeholders clearly and concisely
\item Important commercial and safety decisions are regularly made independently, often employing critical problem solving skills to arrive to a solution
\end{itemize}
}
\emph{Graduate Facilities Engineer} \hfill \texttt{2014 to 2015}

{\footnotesize
As a facilities engineer, I was responsible for various facility assets producing oil and gas, optimising production. Projects were delivered in a timely and economic manner, with deliverables and risks communicated clearly to key stakeholders for approval.

\begin{itemize}
\item Optimisation of gas engines and compressors
\item Project management
\item Risk assessment \\
\end{itemize} }


\textbf{Globe Education Centre}

\emph{Mathematics and Science Tutor} \hfill \texttt{2009 to 2014}
{\footnotesize
\begin{itemize}
\item Tutored students from the ages of 5 to 18 years of age in mathematics and science
\item Supervised individuals and large classes
\end{itemize} }
\HRule


{\footnotesize KEY STRENGTHS}

\begin{itemize}
\item Clear communication skills in time constrained environments,
\item Project management,
\item Collaborative working.
\end{itemize}

\HRule


{\footnotesize REFEREES}

\begin{center}



\begin{tabular}[H]{ r l}
\textbf{\large Lewis Mitchell} & \\[0.3cm]
Organisation: & The University of Adelaide \\
Position: & Associate Professor \\
Email: & lewis.mitchell@adelaide.edu.au \\[1cm]

\textbf{\large Glenn Lydyard} & \\[0.3cm]
Organisation: & Santos Ltd. \\
Position: & Manager Operations Technology (Digital)\\
Email: & glenn.lydyard@santos.com \\[1cm]

\textbf{\large Sungkook Kwon} & \\[0.3cm]
Organisation: & Globe Education Centre \\
Position: & Director \\
Email: & skkwon@gecaustralia.com \\[1cm]

\end{tabular}

\end{center}

\end{document}

